---
title: 'Homework #3'
author: "Ravi Patel; rspatel"
date: "February 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data(tips, package="reshape2")
View(tips)
```

Question 1
```{r}
str(tips)
numParty = 244
```

Question 2:
There are num, Factor, and int types
```{r}
str(tips)
```

Question 3:
```{r}
day <- factor(tips$day, level=c('Thur', 'Fri', 'Sat', 'Sun'))
levels(day)
day
```

Question 4:
```{r}
female5 <- tips[tips$sex == 'Female' & tips$size >= 5, ]
female5
```

Quesiton 5:
The tip seems to have a positive relationship with the the total bill, however there is a large amount of variation in the tip at a given total_bill. One anomily in the data is the total bill beinging near \$33.00 and the tip being near \$1.25. Another anomily is a total bill near \$7.50 and a tip of near \$5.00.
```{r}
library(ggplot2)
ggplot(tips, aes(x=tips$total_bill, y=tips$tip)) + geom_point()
```

Question 6:
The average tip rate is 16.08%
```{r}
tips$tiprate <- tips$tip / tips$total_bill
mean(tips$tiprate)
```

Quseiton 7:
